Word learning at the semantics pragmatics interface

### 2020-04-20 paper/bda_fig.tex
add data distributions to list of eqns, subscript RSA models

\node[det, above=of data_me](L1_me){$L'$};
\node[det, above=of data_comb](L1_comb){$L$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

@@

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5) { 
$\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
 $\rho_i = \text{logistic}(\beta^\rho_0  + i \cdot \beta^\alpha_1)$ \\
$\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ \\
$\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
 $\alpha_i = \beta^\alpha_0  + i \cdot \beta^\alpha_1$ \\
 $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ \\
 $\mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
 $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ \\
 $\sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
 $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0)$ \\
$\beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
 $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$
};

>>>>

\node[det, above=of data_me](L1_me){$L'_{ij}$};
\node[det, above=of data_comb](L1_comb){$L_{ijk}$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

@@

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5.75) { 
$\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
 $\rho_i = \text{logistic}(\beta^\rho_0  + i \cdot \beta^\alpha_1)$ \\
 $d^{CG}_{i} \sim \text{Bernoulli}(\rho_i)$ \\
 \\
$\beta^\alpha_0 \sim \text{Uniform}(-3,3); \beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
 $\alpha_i = \beta^\alpha_0  + i \cdot \beta^\alpha_1$ \\
 \\
 $\mu^\theta_0 \sim \text{Uniform}(-3,3); \mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
 $\sigma^\theta_0 \sim \text{Uniform}(0,2); \sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
 $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0); \beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
 $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$ \\
 $d^{ME}_{ij} \sim L',  d^{CM}_{ij} \sim L$
};
